Research Spike: Evaluation of Using a Single Mnemonic both for Cryptocurrency and Identity Wallets

### 2022-01-17 prism-backend/research/single-mnemonic/discussion.tex
Changes based on Tony's comments.
Added some [non-final] notes on trust registries and secure storage.

From a theoretical point of view, it seems very reasonable to derive all
keys, even for different purposes (payments, staking, or identities) from
the same mnemonic. \secref{ssec:unification}, listed a series of topics
that should be taken into account prior to unifying Cardano and Atala
wallets under the same mnemonic, to avoid security pitfalls. In addition to
those,  there are also some aspects that may need careful consideration, as they
may have impact in the overall security and privacy properties of the wallet
(and related systems).

@@

>>>>

From a theoretical point of view, it seems very reasonable to derive all
keys, even for different purposes (payments, staking, or identities) from
the same mnemonic. \secref{ssec:unification}, listed a series of topics
that should be taken into account prior to unifying Cardano and Atala
wallets under the same mnemonic, to avoid security pitfalls. In addition to
those,  there are also some aspects that may need careful consideration, as they
may have impact in the overall security and privacy properties of the wallet
and related systems.

@@

\paragraph{Secure wallet storage.} %
Currently, Atala has some basic support for encrypted storage%
\footnote{\url{https://github.com/input-output-hk/atala-prism/tree/53f3414a34c88a4a8e54b6d2128d4b14ce2ee8b9/prism-backend/docs/data-vault}
  {\bf WARNING! Internal link.}}, that basically allows storing and
fetching data encrypted with a public key owned by a user. Some secure
storage proposals for cryptocurrency wallets already exist, like Aries's
RFC0050%
\footnote{\url{https://github.com/hyperledger/aries-rfcs/blob/main/concepts/0050-wallets/README.md}
  (last access January 18th, 2022).} or, in a more generic sense,
Identity Foundation's Confidential Storage%
\footnote{\url{https://identity.foundation/confidential-storage} (last access
  January 18th, 2022).}. However, a careful analysis would be needed depending
on the features we want to support (e.g., some sort of generic search on
encrypted data vs just specific types of search), and also the expected
infrastructure (e.g., an oblivious centralized secure storage service vs
multiple user-owned devices that synchronize ``automagically'').
%
Although initially, these may be highly orthogonal topics to the hierarchical
derivation of cryptographic keys, decissions in one domain may affect the other
-- e.g., if we are to implement some sort of forward security mechanism in
an identity wallet, how can we ensure that proper re-encryption is done in
a centralized oblivious secure storage system?

\paragraph{Trust registries.} %
A core component of a decentralized identity system will be one that lets
parties, a priori unknown to each other, derive some sort of trust based on the
system itself. It is reasonable to expect that cryptographic keys (in the
shape of DIDs, or related notions) are used to identify parties in the system,
and assign them some sort of trust metric. As in the topic of secure storage,
this would initially seem an orthogonal issue. But some properties (like, again,
some notion of forward security), may require ad hoc updates of trust registries
in a coordinated manner with an identity wallet -- which might have some
implications into the security analysis.

\paragraph{Are you aware of further challenges that may be worth
  looking into? Have some feedback?} Please, reach out to us:

\begin{itemize}
\item Jesus Diaz Vico (Atala Semantics team).
\item Christos KK Loverdos (Atala Technical Director).
\item Ezequiel Postan (Atala Semantics team).
\item Tony Rose (Atala Head of Product).
\end{itemize}
